\normalfont\spacedallcaps{Hazardous asteroids forecast via Markov random fields}

### 2021-11-30 Manuscript/manuscript.tex
PUB

\chapter{Appendix B: R code}

>>>>

\chapter{Appendix B: R code} Here I provide the code which I run to obtain the results previously showed.  For its writing I took in consideration the examples provided in the  packages documentation, the Prof.Nicolussi lectures and he examples provided in the Hojsgaard textbook  \cite{hojsgaard2012graphical}.
